Ceph Parallel File System Evaluation Report

### 2013-08-23 ceph-initial.tex
split metadata discussion into two: before and after, remove cache mirror subsection

We will describe the efforts and results on performance improvement in the
following sections.

>>>>

\subsection{Metadata Performance Evaluation}

In our particular setup, we only had one metadata server (MDS) configured.
Therefore, this is not a scalability test on the performance of Ceph clustered
MDS, which would have been very interesting.  Instead, we focus on a single MDS
performance and exercise it with up to 8 clients to observe the single MDS
performance scaling. We used mdtest as our benchmark tool. Mdtest parameters
used for this test are:

\begin{itemize}
\item \verb!-w 1048576 -y!: for each created file, we write 1 MB data and
perform a sync operation.  This is a more realistic use case scenario than just
open, close and removal sequence of metadata operations.

\item \verb!-n 1000!: Per client file \textit{and} directory workload. For eight
clients, the total number of files and directories in the workload is 8,000. Since we did not specify
either \verb!-D! or \verb!-F!, this is a mixture of both.

\item \verb!-d /mnt/cephfs/tmp!: we do specify a directory, but unlike under
Lustre file system, where you can have single client multiple mounts (for
increasing workload per client), here we just give the test an explicit home.

\item \verb!-u!: without this option, we are exercising shared directory; with
this option, we are exercising unique directories.

Each test iterates five times and we are presenting the maximum out of all five iterations. 
We summarize the results as follows:

\begin{figure}[htb]
\centering
\includegraphics[width=3in]{data/mdtest-fcreate}
\caption{File creation vs.  number of clients}
\label{fig:mdtest-fcreate}
\end{figure}

\begin{figure}[htb]
\centering
\includegraphics[width=3in]{data/mdtest-dcreate}
\caption{Directory creation vs. number of clients}
\label{fig:mdtest-dcreate}
\end{figure}

%Figure~\ref{fig:mdtest1c} is meant to give an overview on the trending of each
%directory (prefixed with d) and file (prefixed with f) operations, against the
%number of clients. Due to the scale difference, it doesn't convey the
%magnitude of lower numbers.

\item With either shared or unique directory (\verb!-u!), stat
operations for directories and files exhibit strong linear scaling. Same strong
linear scaling is also observed for file read operations.

\item While the other operations seems unaffected or flat by the number of
clients, it is not so if we zoom in, see \ref{fig:mdtest-fcreate} and
\ref{fig:mdtest-dcreate}:  as number of clients increases, we observed the
contention for shared directory. The performance degradation amount to 50\% or
more.

\item Though the same saturation (or degradation) trend was not observed for
file creation operation, it is likely due to lack of workload stress on MDS.

The results also show that file creation rate is signficantly lower than
directory creation rate. We stipulated two contributing factors: one is the file
creation is associated with 1 MB data write and followed by a fsync operation,
which is a rather heavy weight operation compare to directory creation. Another
factor is that we obtained above results while both RADOS and file
system-level performance are not tuned for optimal, yet.

Next, we will describe the efforts and results on performance improvement at
both RADOS and file system-level. As consequence, we expect to see improved
metadata performance as well.

### 2013-08-23 ceph-tuning.tex
add paper flow and organization into introduction
split metadata discussion into two: before and after, remove cache mirror subsection

\section{Improving RADOS Performance}

@@

\subsection{Disable Cache Mirroring on Controllers}

@@

\subsection{Disable TCP autotuning}

@@

\begin{Verbatim}
     echo 0 | sudo tee /proc/sys/net/ipv4/tcp_moderate_rcvbuf
\end{Verbatim}

@@

\subsection{Repeating RADOS Scaling Test}

@@

\section{Improving Ceph File System Performance}
\label{sec:improve-ior}

@@

\subsection{Disabling Client CRC32}

@@

\begin{Verbatim}
mount -t ceph 10.37.248.43:6789:/ /mnt/ceph -o name=admin,nocrc
\end{Verbatim}

@@

\subsection{Improving IOR Read Performance}

@@

\begin{Verbatim}[samepage=true]
mount -t ceph 10.37.248.43:6789:/ /mnt/ceph -o
   name=admin,nocrc,readdir_max_bytes=4104304,readdir_max_entries=8192
\end{Verbatim}

@@

\subsection{Repeating the IOR Scaling Test}

@@

>>>>

\section{Tuning, Optimization and Improvements}
\label{sec:ceph-tuning}

\subsection{Improving RADOS Performance}

@@

\begin{comment}

\subsubsection{Disable Cache Mirroring on Controllers}

@@

\end{comment}

\subsubsection{Disable TCP autotuning}

@@

\begin{Verbatim}[fontsize=\small]
 echo 0 | sudo tee 
   /proc/sys/net/ipv4/tcp_moderate_rcvbuf
\end{Verbatim}

@@

\subsubsection{Repeating RADOS Scaling Test}

@@

\subsection{Improving Ceph File System Performance}
\label{sec:ceph-tuning-fs}

@@

\subsubsection{Disabling Client CRC32}

@@

\begin{Verbatim}[fontsize=\small]
mount -t ceph 10.37.248.43:6789:/ 
    /mnt/ceph -o name=admin,nocrc
\end{Verbatim}

@@

\subsubsection{Improving IOR Read Performance}

@@

\begin{Verbatim}[samepage=true, fontsize=\small]
mount -t ceph 10.37.248.43:6789:/ 
  /mnt/ceph -o name=admin,nocrc,
  readdir_max_bytes=4104304,
  readdir_max_entries=8192
\end{Verbatim}

@@

\subsubsection{Repeating the IOR Scaling Test}

@@

\subsection{Revisit Metadata Performance}

Our previous results show that file creation rate is significantly lower than
directory creation rate. Also, we conjectured two reasons: one is the file
creation is associated with 1 MB data write and followed by a fsync operation.
Another reason being that we obtained above results from early version of Ceph
without all the tunings and improvement applied.

Therefore, we repeated the same test on the latest CephFS 0.64. The result is
illustrated in Figure~\ref{fig:mdtest-064-file-create}. As expected, we
observed a significant improvement on the file creation rate. We also note
that as number of clients increase, the file creation rate decreases rapidly,
which suggested some form of lock contention. This presents some interesting
issues to be investigated further.

\begin{figure}[htb]
\centering
\includegraphics[width=3.5in]{mdtest-064-file-create}
\caption{mdtest of file creation on Ceph 0.64}
\label{fig:mdtest-064-file-create}
\end{figure}
